\documentclass[a4paper]{exam}

\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{titling}

\printanswers

\title{Weekly Challenge 02: Polycarp's Permutation!}
\author{$\langle team-name \rangle$}  % <== for grading, replace with your team name, e.g. q1-team-420
\date{Habib University | Spring 2023}

\qformat{{\large\bf \thequestion. \thequestiontitle}\hfill}
\boxedpoints

\begin{document}
\maketitle

\begin{questions}

    \titledquestion{Lost Permutation}
    Once upon a time, in a faraway land, there lived a young mathematician named Polycarp.
    He loved solving problems and was particularly fond of permutations. He would often
    spend hours creating and manipulating different permutations to see what kind of
    patterns he could find.

    One day, while working on a particularly challenging problem, Polycarp got so caught up
    in his work that he didn't realize how much time had passed. When he finally looked up,
    it was dark outside and he realized that he had lost his favorite permutation. Frantic,
    he searched through his papers and notebook, but it was nowhere to be found.Feeling
    defeated, Polycarp decided to try and recreate his permutation by using the numbers
    that he could remember. He had written down the integers $\mathbf{a_1, a_2, \cdots , a_m}$
    but he couldn't remember the rest of the permutation.  However, he is certain that
    sum of the numbers he lost is $\mathbf{S}$.

    Can you find a way to add numbers to the sequence $\mathbf{a_1,a_2,\cdots, a_m}$ that he has
    so that the sum of the added numbers equals $\mathbf{S}$, and the resulting array is a permutation.




    \paragraph{Task}
    \begin{itemize}
        \item Implement solution for the Polycarp's problem in the accompanying file,  \texttt{permutation.py}.
              We wish to know if the \textbf{lost permutation} exists, i.e., if you can append several numbers to the array \textbf{a}, which sum to $\mathbf{S}$ exactly and the sequence will become a permutation. 

        \item A sequence of n numbers is called a permutation if it contains all integers from $1$ to $n$
              exactly once. For example, the sequences $[3,1,4,2], [1]$  and $[2,1]$ are permutations, but $[1,2,1]$,
              $[0,1]$ and $[1,3,4]$ — are not.

    \end{itemize}


    \paragraph{Input}

    \begin{itemize}
        \item The first line of the input contains a number $n$ denoting the number of testcases. This is followed by $n$ testcases, each containing two lines. We have integers $\mathbf{m}$ and $\mathbf{S}$ in the first line of testcase where $ 1 \leq m \leq 100 $,$1 \leq S \leq 10000 $.
        \item For a testcase, $\mathbf{m}$ is the number of found elements and $\mathbf{S}$ the sum of forgotten numbers. The second line of each testcase contains $\mathbf{m}$ \textbf{different integers} $a_1,a_2, \cdots, a_m$ where $1 \leq a_i \leq 100$ are the elements Polycarp managed to find.
    \end{itemize}

    \paragraph{Output}
    \begin{itemize}
        \item Output will contain several lines with $i$th line denoting the answer for $i$th testcase. The answer is \textbf{YES} if you can append several elements to the array \textbf{a}, such that their sum equals $\mathbf{S}$ and the resultant array is a permutation. Otherwise, the answer is \textbf{NO}.
    \end{itemize}

    \paragraph{Examples}
    \begin{itemize}
        \item For example, when $\mathbf{m}=3 ,\mathbf{S}=13,\mathbf{a}=[3,1,4]$. You can append to $\mathbf{a}$ the numbers $6,2,5,$ the sum of which is $6+2+5=13$. Note that the permutation $[3,1,4,6,2,5]$ exists so the answer for this case is \textbf{YES}.
        \item For example, when $\mathbf{m}=3 ,\mathbf{S}=17,\mathbf{a}=[1,3,7]$. You can append to $\mathbf{a}$ the numbers $2,4,5,6$ the sum of which is $2+4+5+6=17$. Note that the permutation $[1,3,7,2,4,5,6]$ exists so the answer for this case is \textbf{YES}.
        \item For example, when $\mathbf{m}=3 ,\mathbf{S}=17,\mathbf{a}=[2,4,5]$. You can append to $\mathbf{a}$ the numbers $1,3,6,7$ the sum of which is $1+3+7+6=17$. Note that the permutation $[2,4,5,1,3,6,7]$ exists so the answer for this case is \textbf{YES}.
        \item For example, when $\mathbf{m}=1 ,\mathbf{S}=1,\mathbf{a}=[1]$. You cannot append one or more numbers to $\mathbf{a}$ such that their sum equals $1$ and the result is a permutation. Consequently, the answer is \textbf{NO}
        \item For example, when $\mathbf{m}=3 ,\mathbf{S}=17,\mathbf{a}=[2,3,1]$. You can append to $\mathbf{a}$ the numbers $2,4,5,6$ the sum of which is $2+4+5+6=17$. The result is equal to $[2,3,1,2,4,5,6]$ but this not a valid permutation as $2$ is repeated. Consequently,  the answer is \textbf{NO}
        
    \end{itemize}
   

\end{questions}

\end{document}
